\section{Novel Method For Finding The Distance Spectrum}
\label{sec4}
In this section, we present our novel method for obtaining what we have named the \textit{structured distance spectrum}. Our novel method can be seen to be the combination of two different but related methods. The first method is quite simple and makes use the fact that in the polynomial domain, RTZ inputs and their corresponding parity-check sequences share a common factor. 
The second method shows how to obtain this common factor when the weight of the RTZ input or its parity-check sequence is fixed for a given RSC code. 
After explaining the inner working of our novel method, we use it to obtain the partial structured distance spectrum for the $5/7,~ 37/21$ and $23/35$  RSC codes.

Throughout this section, the symbols $\bb,~\bh$ and $\bc$ represent the input message, parity-check sequence and the codeword respectively in vector form whiles $b(x),~h(x)$ and $c(x)$ are their equivalent polynomial representation. We use the  polynomial r(x) when there is no need to distinguish between $b(x)$ and $h(x)$. Also when we need to refer to $g(x)$ and $h(x)$ in general terms we use the polynomial $q(x)$. $\br~ \text(and) ~\bq$ refer to their corresponding vector representations.

\subsection{Low-weight Codewords}
%(quarantine)%The distance spectrum derived via the transfer function method is an insufficient tool when it comes to to interleaver design. In this section, we present a novel method that generates what we refered to as the structured distance spectrum, which is the distance spectrum with the structure of the RTZ inputs as well as the corresponding parity-check sequence revealed, therefore making it a very useful tool for interleaver design.

%(quarantine)%For an RSC code, the Hamming weight of the codeword $w_H(\bc)$ is the sum of the weights of the parity bit sequence and message input. 
In polynomial notation, the parity-check sequence can be expressed as 
\begin{equation}
h(x) =f(x)\cdot g^{-1}(x)\cdot b(x)
\label{novelEq0}
\end{equation}
If we consider large frame sizes, the prescence of $g^{-1}(x)$ means that within $h(x)$ is a particular sequence of bits which is repeated a large number of times. This results in a large parity weight and with a high probability, leads to a codeword with a high weight. The only time this is not the case is when
\begin{equation}
b(x) \bmod g(x) \equiv 0
\label{novelEq1}
\end{equation}
This results in a relatively low-weight parity bit sequence which might produce a low-weight codeword. Any $b(x)$ that meets the condition in (\ref{novelEq1}) can be written as 
\begin{equation}
b(x) =a(x)g(x)
\label{novelEq2}
\end{equation}
where $a(x)$ is a monic polynomial with the coefficient of the lowest term not equal to $0$.
Fixing $b(x)$ from (\ref{novelEq2}) into (\ref{novelEq2}) we have 
\begin{equation}
\begin{split}
h(x)&=f(x)\cdot g^{-1}(x)\cdot a(x)g(x)\\
&=a(x)f(x)
\end{split}
\label{novelEq3}
\end{equation}
%(quarantine)%Using both (\ref{novelEq2})  and (\ref{novelEq3}), we wish to list all low-weight codewords for a given RSC code.A low-weight codeword is any codeword which satisfies the condition, $w_H(\bc) \leq d_{\text{max}}$. This list is known as the \textit{partial structured distance spectrum}. To generate the partial structured distance spectrum, we take note of a few things. 
From (\ref{novelEq2})  and (\ref{novelEq3}), we observe that $a(x)$ is a common factor in both equations and if we are able to solve for $a(x)$ via either of the equations, the remaining equation can be solved. To solve for $a(x)$ requires that in either equations it should be the only unknown variable. At first glance it might seem like $g(x)$ and $h(x)$ are the only known variables since they are dependent on the RSC code in question. However, is we remember that the weight of $h(x)$ and $b(x)$ is directly proportional to the number of terms it has, then we are on our way to obtaining our second known variable. All that stands in our way is determining valid power values for the polynomial  terms, depending on the weight of $h(x)$ or $b(x)$.

Revisiting (\ref{novelEq3}), we see that $h(x)$ is divisible by both $f(x)$ and $a(x)$ and therefore their roots are also the roots of $h(x)$. However, since the value of $a(x)$ is variable, we will use the root of $f(x)$ when determining  the valid power values for the polynomial  terms of $h(x)$ for a given weight value. Similarly, $b(x)$ is also divisible by $a(x)$ and $g(x)$ (from (\ref{novelEq2})) but we utilize the roots of $g(x)$ when determining the valid power values for the polynomial  terms of  $b(x)$ for a given weight value.  
Having determined the values of $h(x)$ or $b(x)$ for a fixed Hamming weight value and RSC code, we can now generate the partial structured distance spectrum for that RSC code. Beginning with (\ref{novelEq2}), we  solve for $a(x)$ for a predetermined number of valid values of $b(x)$ and then use $a(x)$ in (\ref{novelEq3}) to obtain the corresponding value of $h(x)$. Since there is no guarantee that low-weight message inputs always map to low-weight parity-check sequences, we repeat the same operation obtaining $a(x)$ via (\ref{novelEq3}) for a predetermined number of valid values of $h(x)$ and then use $a(x)$ in (\ref{novelEq2}) to obtain the corresponding value of $b(x)$. From the lists obtained from both operations, we can then generate the partial structured distance spectrum by selecting $h(x)$ and $b(x)$ values $\st w_H(\bc) \leq d_{\text{max}},~d_{\text{max}}=d_{\text{free}}+3$.

\subsection{Finding Valid Values of $h(x)$ and $b(x)$ for a Fixed Hamming Weight and RSC Code}
We have established that the relationship between the roots of $f(x)$ and $h(x)$ as well as the relationship between the roots of $g(x)$ and $b(x)$. Depending on the characteristic makeup of $f(x)$ , we can easily determine the structure of $h(x)$ for the its different weight values. The same logic applies to determining the structure of $b(x)$ for its different weight values from $g(x)$. 
We therefore present a method for determining valid values of $h(x)$ and $b(x)$ for a given RSC code when the weight values $w_H(\bh),~w_H(\bb) \leq 3$. We state here that there is no RTZ input of weight 1, since it goes against the definition of RTZ inputs.Consequently, there also cannot be a corresponding parity-check sequence of weight 1 and we can ignore those cases. 
The characteristic makeup of both $f(x)$ and $g(x)$ can be grouped into the 4 cases below. 
\begin{enumerate}
\item Single primitive polynomial.
\item Prime but not a primitive polynomial.
\item Made up of equal repeated polynomial roots.
\item Made up of unique repeated polynomial roots.
\end{enumerate}
Since there is no difference between the general structure of $h(x)$ and $b(x)$ once the Hamming weight is fixed, we use $q(x)$ to represent either of them.  If we fix $r(x)$ into (\ref{novelEq3}) or (\ref{novelEq3}), then $f(x)$ will be equivalent to$g(x)$ so we will use $r(x)$ to represent either of them. 
\newpage
\subsubsection{Structure of $q(x),~w_H(\bq) =2$ }
It is obvious that the structure of $q(x)=1+x^a$ when $w_H(\bh) =2$. What remains is finding the right value for $a$.
\paragraph{ Case1: $r(x)$ is a single primitive polynomial \newline }
Since $r(x)$ is a prime polynomial, it has a primitive element $\beta$ as its root, which means $\beta$ is also a root of $q(x)=1+x^a$. Substituting $\beta$ into the equation, we have 
\begin{equation}
\begin{split}
1+\beta^a=&0\\
\beta^a=&1
\end{split}
\end{equation}
For any primitive polynomial that generates the extended field GF$(2^m),~\beta^{2^{m}-1}=1$
which means any valid of $a$ should satisfy the condition below.
$$2^{m}-1~|~a$$

\paragraph{ Case2: $r(x)$ is prime polynomial but not primitive \newline}
Similar to the case for primitive polynomials, there is a value $j < 2^m-1$ such that 
$$\beta^j=1,~j~|~2^{m}-1 $$. Therefore any valid value of $a$ should satisfy the condition below.
$$j~|~a$$

\paragraph{ Case3: $r(x)$ is made up of equal repeated polynomial roots.\newline}
Given the above condition we have, $r(x)=(r^{o_p}_p(x))^k$, where $r^{o_p}_p(x)$ represents the prime polynomial $r(x)$ can be factorized into and $k$ is the number of times it is repeated. $r^{o_p}_p(x)$ has $\beta$ as its roots and we need to find $d \st \beta^j=1$ in the (extended) field it generates. Since $\beta^{kj}=1$ in that same (extended) field , the valid values for $a$ should satisfy the condition below
$$kj ~| ~a$$

\paragraph{Case4: $r(x)$ is made up of unique repeated polynomial roots. \newline}
We may write $r(x)$ as $$r(x)=\prod_{k=1}^{K}r^{o_k}_k(x)$$ The $kth$ polynomial is prime and has a value $d_k \st \beta^{j_k}=1$. Since each value of $j_k$ is unique, valid values of $a$ should satisfy the condition below. 

$$ \bigcap_{k=1}^{K} \{j_k~| a\}$$
%=========Examples===============%

\newpage

\begin{example}
$5/7$ RSC Code $f(x)=1+x^2,~g(x) = 1+x+x^2$\newline
$f(x)$ is a match for Case3, ie it is made up of equal repeated polynomial roots. It can be written as $$f(x)=(1+x)^2,~k=2$$ $1+x$ is prime in $GF(2)$ and $\beta^{1}=1$. Since $k=2$, we have $\beta^{k}=\beta^{2}=1$. $h(x)=1+x^a$ and the valid values of $a=\{2,4,6,\cdots \}$.
The corresponding values for $a(x),~b(x)$ and $h(x)$ are shown in the table below for the first 4 valid values of $a$

 \begin{table*}[h]
 \caption{$5/7$ RSC Code, $f(x)=1+x^2$}
\centering
 \begin{tabular}{c c c} 
 \hline
 $a(x)$ & $b(x)$ & $h(x)$ \\ [0.5ex] 
 \hline\hline
$1$ & $1+x+x^2$ & $1+x^2$ \\ 
$1+x^2$ & $1+x+x^3+x^4$ & $1+x^{4}$  \\
$1+x^2+x^4$ & $1+x+x^3+x^5+x^6$ & $1+x^{6}$  \\
$1+x^2+x^4+x^6$ & $1+x+x^3+x^5+x^7+x^8$ & $1+x^{8}$  
 \end{tabular}
 \label{novelTab1}
\end{table*}

$g(x)$ is a match for Case1, ie it is a primitive polynomial for GF$(2^2)$. In this extended field, $\beta^{3}=1$. $b(x)=1+x^b$ and the valid values of $b$ are $b=\{3,6,9,\cdots \}$. The corresponding values for $a(x),~b(x)$ and $h(x)$ are shown in the table below for the first 4 valid values of $b$.

 \begin{table*}[h]
 \caption{$5/7$ RSC Code, $g(x)=1+x+x^2$}
\centering
 \begin{tabular}{c c c} 
 \hline
 $a(x)$ & $b(x)$ & $h(x)$ \\ [0.5ex] 
 \hline\hline
$1+x$ & $1+x^{3}$ &$1+x+x^2+x^3$\\
\hline
$1+x+x^3+x^4$ & $1+x^{6}$ &$1+x+x^2+x^4+x^5+x^6$ \\
\hline
$1+x+x^3+x^4+x^6+x^{7}$ &  $1+x^{9}$ &$1+x+x^2+x^4+x^5+x^7+x^8+x^9$\\
\hline
$1+x+x^3+x^4+x^6+x^{7}+x^9+x^{10}$ &  $1+x^{12}$ &$1+x+x^2+x^4+x^5+x^7+x^8+x^{10}+x^{11}+x^{12}$\\
 \end{tabular}
 \label{novelTab2}
\end{table*}
\end{example}


%=======37/21 RSC=========%
\begin{example}
$37/21$ RSC Code, $f(x)=1+x+x^2+x^3+x^4,~g(x)=1+x^4$\newline
$f(x)$ is a match for Case2, ie it is a prime polynomial but not primitive. It can be used to generate GF$(2^4)$ and in the field it generates, $\beta^{5}=1$. Therefore, the valid values of $a$ are $a=\{5,10,15,\cdots\}$. The corresponding values for $h(x)$ and $a(x)$ are shown in the table below for the first 4 valid values of $a$.

 \begin{table*}[h]
 \caption{$37/21$ RSC Code, $f(x)=1+x+x^2+x^3+x^4$}
\centering
 \begin{tabular}{c c c} 
 \hline
 $a(x)$ & $b(x)$ & $h(x)$ \\ [0.5ex] 
 \hline\hline
$1+x$ &$1+x+x^4+x^5$ &  $1+x^5$\\ 
$1+x+x^5+x^6$ &$1+x+x^4+x^6+x^9+x^{10}$ & $1+x^{10}$ \\
$1+x+x^5+x^6+x^{10}+x^{11}$ & $1+x+x^4+x^6+x^9+x^{11}+x^{14}+x^{15}$ & $1+x^{15}$ \\
$1+x+x^5+x^6+x^{10}+x^{11}+x^{15}+x^{16}$ &$1+x+x^4+x^6+x^9+x^{11}+x^{14}+x^{16}+x^{19}+x^{20}$ & $1+x^{20}$ 
 \end{tabular}
 \label{novelTab3}
\end{table*}

$g(x)$ is a match for Case3, ie it is made up of equal repeated polynomial roots. It can be written as $$g(x)=(1+x)^4,~k=4$$ $1+x$ is prime in $GF(2)$ and $\beta^{1}=1$. Since $k=4$, we have $\beta^{k}=\beta^{4}=1$. $b(x)=1+x^b$ and the valid values of $b=\{4,8,12,\cdots \}$.
The corresponding values for $a(x),~b(x)$ and $h(x)$ are shown in the table below for the first 4 valid values of $a$

 \begin{table*}[h]
 \caption{$37/21$ RSC Code, $g(x)=1+x^4$}
\centering
 \begin{tabular}{c c c} 
 \hline
 $a(x)$ & $h(x)$ \\ [0.5ex] 
 \hline\hline
$1$ &  $1+x^4$ & $1+x+x^2+x^3+x^4$\\ 
$1+x^4$ & $1+x^{8}$ & $1+x+x^2+x^3+x^5+x^6+x^7+x^8$ \\
$1+x^4+x^8$ & $1+x^{12}$ & $1+x+x^2+x^3+x^5+x^6+x^7+x^9+x^{10}+x^{11}+x^{12}$\\
$1+x^4+x^8+x^{12}$ & $1+x^{16}$ & $1+x+x^2+x^3+x^5+x^6+x^7+x^9+x^{10}+x^{11}+x^{13}+x^{14}+x^{15}+x^{16}$
 \end{tabular}
 \label{novelTab4}
\end{table*}

\end{example}
%===========23/35 RSC=========%
\begin{example}
$23/35$ RSC Code, $f(x)=1+x+x^4,~g(x)=1+x^2+x^3+x^4$\newline
$f(x)$ is a match for Case1, ie it is a primitive polynomial which can be used to generate the extended field GF$(2^4)$. In this field, $\beta^{15}=1$. $h(x)=1+x^a$ and the valid values of $a$ are $a=\{15,30,45,\cdots \}$. The corresponding values for $a(x),~b(x)$ and $h(x)$ are shown in the table below for the first 2 valid values of $a$.

 \begin{table*}[h!]
 \caption{$23/35$ RSC Code, $f(x)=1+x+x^4$}
\centering
 \begin{tabular}{p{7cm} | p{7cm} | c} 
 \hline
 $a(x)$ & $b(x)$ & $h(x)$ \\ [0.5ex] 
 \hline\hline
$1+x^2+x^3+x^5+x^7+x^8+x^{11}$ 
& $1+x+x^3+x^4+x^7+x^{11}+x^{12}+x^{13}+x^{14}+x^{15}$ 
&$1+x^{15}$\\ 
\hline
$1+x^2+x^3+x^5+x^7+x^8+x^{11}+x^{15}+x^{16}+x^{17}+x^{18}+x^{20}+x^{22}+x^{23}+x^{26}$ 
&$1+x+x^3+x^4+x^7+x^{11}+x^{12}+x^{13}+x^{14}+x^{16}+x^{18}+x^{19}+x^{22}+x^{26}+x^{27}+x^{28}+x^{29}+x^{30}$ 
&$1+x^{30}$\\
 \end{tabular}
 \label{novelTab5}
\end{table*}

$g(x)$ is a match for Case4, ie it is made up of unique repeated polynomial roots. It be written as $$g(x)=(1+x)(1+x+x^3),~K=2$$
 $1+x$ is prime in $GF(2^1)$ and $\beta^{1}=1$. $1+x+x^3$ is prime in $GF(2^3)$ and $\beta^{7}=1$. $b(x)=1+x^b$ and consequently, the valid values of $b$ that meet the condition $$ \bigcap_{k=1}^{K} \{j_k~| b\}$$ are $b=\{7,14,21,\cdots \}$.
The corresponding values for $a(x),~b(x)$ and $h(x)$ are shown in the table below for the first 4 valid values of $b$

\begin{table*}[h]
 \caption{$23/35$ RSC Code, $g(x)=1+x^2+x^3+x^4$}
\centering
 \begin{tabular}{p{6cm}| c | p{8cm}} 
 \hline
 $a(x)$ & $b(x)$ & $h(x)$ \\ [0.5ex] 
 \hline\hline
$1+x^2+x^3$ & $1+x^7$ &$1+x+x^2+x^6+x^7$\\ 
\hline
$1+x^2+x^3+x^7+x^9+x^{10}$ &  $1+x^{14}$ &$1+x+x^2+x^6+x^8+x^9+x^{13}+x^{14}$\\
\hline
$1+x^2+x^3+x^7+x^{9}+x^{10}+x^{14}+x^{16}+x^{17}$ & $1+x^{21}$ 
&$1+x+x^2+x^6+x^8+x^9+x^{13}+x^{15}+x^{16}+x^{20}+x^{21}$\\
\hline
$1+x^2+x^3+x^7+x^{9}+x^{10}+x^{14}+x^{16}+x^{17}+x^{21}+x^{23}+x^{24}$ & $1+x^{28}$ &$1+x+x^2+x^6+x^8+x^9+x^{13}+x^{15}+x^{16}+x^{20}+x^{22}+x^{23}+x^{27}+x^{28}$
 \end{tabular}
 \label{novelTab6}
\end{table*}

\end{example}







\newpage
%\begin{example}
%$f(x)=1+x^2+x^3+x^4$\newline
%$f(x)$ is reducible and can be written as $$f(x)=(1+x)(1+x+x^3),~K=2$$
 %$1+x$ is prime in $GF(2^1)$ and $\beta^{1}=1$. $1+x+x^3$ is prime in $GF(2^3)$ and $\beta^{7}=1$ Consequently, the valid values of $a$ that meet the condition $$ \bigcap_{k=1}^{K} \{j_k~| a\}$$ are $a=\{7,14,21,\cdots \}$.
%The corresponding values for $h(x)$ and $a(x)$ are shown in the table below for the first 4 valid values of $a$

%\begin{table*}[h]
 %\caption{$f(x)=1+x^2+x^3+x^4$}
%\centering
 %\begin{tabular}{c c} 
% \hline
 %$a(x)$ & $h(x)$ \\ [0.5ex] 
% \hline\hline
%$1+x^2+x^3$ & $1+x^7$\\ 
%\hline
%$1+x^2+x^3+x^7+x^9+x^{10}$ &  $1+x^{14}$ \\
%\hline
%$1+x^2+x^3+x^7+x^{9}+x^{10}+x^{14}+x^{16}+x^{17}$ & $1+x^{21}$ \\
%\hline
%$1+x^2+x^3+x^7+x^{9}+x^{10}+x^{14}+x^{16}+x^{17}+x^{21}+x^{23}+x^{24}$ & $1+x^{28}$ 
% \end{tabular}
% \label{novelTab4}
%\end{table*}

%\end{example}


\newpage


\subsubsection{Structure of $q(x),~w_H(\bq) =3$}

Again, it is obvious that $q(x)=1+x^u+x^v,=v\neq u$ and given $r(x)$, our task is to find valid values for $u$ and $v$. If there are no values for the pair $(u,v)$, then $q(x) \st w_H(\bq) =3$ does not exist for the given $r(x)$.
% It is worth noting that such $h(x)$ only exist iff $f(x)$ has exactly $w_H(\bh) =3$ terms. Moving forward, we assume that for all the cases, this condition holds true.
\paragraph{ Case1: $r(x)$ is a single primitive polynomial \newline}
Since $r(x)$ is a prime polynomial, it has a primitive element $\beta$ as it root, which means $\beta$ is also a root of $q(x)=1+x^u+x^v$. Substituting $\beta$ into the equation, we have 
\begin{equation}
\begin{split}
1+\beta^u+\beta^v=&0\\
\beta^u+\beta^v=&1
\end{split}
\end{equation}
where $u\neq v$
For any extended field GF$(2^m),~m >1$, there are exactly $q=2^{(m-1)}-1 ~(e,f)$ pairs $\st \beta^e+\beta^f=1,~e\neq f$. This can easily be confirmed from the table of elements representing GF$(2^m)$. If we represent the set of $(e,f)$ pairs as 
$\bz=\{ (e_1,f_1) , e_2,f_2),\cdots,(e_1,f_q)\} $, then any valid value for $u$ and $v$ should satisfy the condition
$$(u,v) \equiv (e,f) \bmod 2^m-1,~(e,f)\in \bz$$ since $\beta^{2^{m}-1}=1$

\paragraph{Case2: $r(x)$ is prime but not a primitive polynomial\newline}
A prime but not primitive polynomial generates an (extended) field with $j$ elements, where $j<2^m-1$. Similar to the case where $r(x)$ is primitive, we confirm the existence of $(e,f)$ pairs $ \st \beta^e + \beta^f =1$. 
If we represent the set of $(e,f)$ pairs as 
$\bz=\{ (e_1,f_1) , e_2,f_2),\cdots,(e_1,f_q)\} $, then any valid value for $u$ and $v$ should satisfy the condition
$$(u,v) \equiv (e,f) \bmod j,~(e,f)\in \bz$$ since $\beta^{j}=1$

\paragraph{Case3: $r(x)$ is made up of equal repeated polynomial roots\newline}
For this case, we can write $r(x)$ as 
$r(x)=(r^{o_p}_p(x))^k$, where $r^{o_p}_p(x)$ represents the prime polynomial that is the root of $r(x)$ and $k$ is the number of times it is repeated. If $r^{o_p}_p(x)$ is a primitive polynomial and $m>1$, then from Case1 there are exactly $q=2^{(m-1)}-1~(e,~f)$ pairs $\st \beta^e+\beta^f=1,~e \neq f$ in the set $\bz$. 
If $r^{o_p}_p(x)$ is prime but not a primitive polynomial, then we determine the number of elements in the set $\bz$ directly from the table representing the field it generates.
 If we focused on $f^{o_p}_p(x)$ only, $(u',v')$ should satisfy the condition$$ (u',v') \equiv (e,f)\bmod 2^{m}-1,~(e, f) \in \bz$$. However, since $f(x)$ is made up of $f^{o_p}_p(x)$ repeated $k$ times, and $\beta^{ke}+\beta^{kf}=1$, the valid values for $u$ and $v$
 should satisfy the condition
 $$(u,v)=(ku',kv'),~(u,v) \equiv (e,f)\bmod 2^{m}-1,~(e, f) \in \bz $$

\paragraph{Case4 $r(x)$ is made up of unique repeated polynomial roots\newline}
We may write $r(x)$ as $$r(x)=\prod_{k=1}^{K}r^{o_k}_k(x)$$ 
For the $kth$ polynomial, we refer to the (extended) field table and determine if there exists any $(e^{(k)},~f^{(k)})$ pairs $\st \beta^{e^{(k)}}+\beta^{f^{(k)}}=1$. If it exists for all $K$ polynomials, then the valid values for $u$ and $v$
 should satisfy the condition

 $$\textcolor{red}{\bigcap_{k=1}^{K} (u,v)=(ku',kv'),~(u,v) \equiv (e^{(k)},f^{(k)})\bmod 2^{m}-1,~(e^{(k)}, f^{(k)}) \in \bz^{(k)}} $$



\begin{example}
$5/7$ RSC Code, $f(x)=1+x^2,~g(x)=1+x+x^2$\newline
$f(x)$ is a match for Case3 and can be written as $(1+x)^2$. $(1+x)$ is a primitive polynomial for GF$(2)$. The elements of GF$(2)$ are shown in Table \ref{} and in this field, there are no valid $(e,f)$. Therefore, $h(x) \st w_H(\bh)=3$ does not exist.

$g(x)$ is a match for Case1, ie it is a primitive polynomial for GF$(2^2)$ with $\beta^{3}=1$. 
The elements of GF$(2^2)$ are shown in Table \ref{novelTab5} and it is obvious that there is exactly 1 ($q=2^{(2-1)}-1~=1$) valid $(e,f)$ pair $\st \beta^e+\beta^f = 1$ and that is $(1,2)$.
Which means the valid values of $(u,v)$ pairs are any values $\st (u,v) \equiv (1,2) \bmod 3$.  The corresponding values for $a(x),~b(x)$ and $h(x)$ are shown in the table below for the first 4 valid values of $(u,v)$

 \begin{table*}[h]
 \caption{Non-zero Elements of GF$(2^2)$ generated by $g(x)=1+x+x^2$}
\centering
 \begin{tabular}{c c} 
 \hline
 power representation & actual value \\ [0.5ex] 
 \hline\hline
$\beta^0~=\beta^3=1$ & $1$\\
\hline
$\beta$ & $\beta$\\
\hline
$\beta^2$ &  $1+\beta$\\
 \end{tabular}
 \label{novelTab7}
\end{table*}

\begin{table*}[h]
 \caption{$5/7$ RSC, $g(x)=1+x+x^2$}
\centering
 \begin{tabular}{c c c} 
 \hline
 $a(x)$ & $b(x)$ & $h(x)$\\ [0.5ex] 
 \hline\hline
$1$ & $1+x+x^2$ & $1+x^2$\\ 
\hline
$1+x+x^2$ &  $1+x^2+x^4$ & $1+x+x^3+x^4$ \\
\hline
$1+x+x^3$ & $1+x^4+x^5$ & $1+x+x^2+x^5$\\
\hline
$1+x^2+x^3$ & $1+x+x^5$  &$1+x^3+x^4+x^5$
 \end{tabular}
 \label{novelTab8}
\end{table*}
\end{example}

\newpage

 
 \begin{example}
$37/21$ RSC Code, $f(x)=1+x+x^2+x^3+x^4,~g(x)=1+x^4$\newline
$f(x)$ is a match for Case2, ie it is a prime but not primitive polynomial. From the table of the extended field generated by $f(x)$ (Table \ref{novelTab9}), we see that there are no valid $(e,~f)$ and as such $h(x) \st w_H(\bh)=3$ is non-existent.


 \begin{table*}[h]
 \caption{Non-zero Elements of GF$(2^2)$ generated by $f(x)=1+x+x^2+x^3+x^4$}
\centering
 \begin{tabular}{c c} 
 \hline
 power & polynomial \\ [0.5ex] 
 \hline\hline
$\beta^0~=\beta^5=\beta^{10}=\beta^{15}=1$ & $1$\\
\hline
$\beta=\beta^6=\beta^{11}$ & $\beta$\\
\hline
$\beta^2=\beta^7=\beta^{12}$ &  $\beta^2$\\
\hline
$\beta^3=\beta^8=\beta^{13}$ &  $\beta^3$\\
\hline
$\beta^4=\beta^9=\beta^{14}$ &  $\beta^3+\beta^2+\beta+1$\\
 \end{tabular}
 \label{novelTab9}
\end{table*}

$g(x)$ is a match for Case3, ie it is made up of equal repeated roots. After factorization, we have $g(x)=(1+x)^4. $(1+x) is a primitive polynomial which generates the field GF$(2)$ and in this field, there are also no valid $(e,~f)$ and as such $b(x) \st w_H(\bb)=3$ is also non-existent.
\end{example}
 
\begin{example}
$23/35$ RSC Code, $f(x)=1+x+x^4,~g(x)=1+x^2+x^3+x^4$ \newline
$f(x)$ is a match for Case1, ie it is a primitive polynomial which can be used to generate the extended field GF$(2^4)$ with $\beta^{15}=1$.. The elements of GF$(2^4)$ are shown in Table \ref{novelTab10} and we can see that there are $7$ valid $(e,f)$ pairs
 
 Which means the valid values of $(u,v)$ pairs are any values $\st (u,v) \equiv (e,f) \bmod 15, (e,f) \in \bz,~\bz=\{(1,4),~(2,8) ,~(3,14) ,~(5,10) ,~(6,13) ,~(7,9) ,~(11,12))$.
 The corresponding values for $a(x),~b(x)$ and $h(x)$ are shown in the Table \ref{novelTab11} below for the first 4 valid values of $(u,v)$
 
  \begin{table*}[h]
 \caption{Non-zero Elements of GF$(2^4)$ generated by $f(x)=1+x+x^4$}
\centering
 \begin{tabular}{c c} 
 \hline
 power & polynomial \\ [0.5ex] 
 \hline\hline
$\beta^0~=\beta^{15}=1$ & $1$\\
\hline
$\beta$ & $\beta$\\
\hline
$\beta^2$ &  $\beta^2$\\
\hline
$\beta^3$ & $\beta^3$\\
\hline
$\beta^4$ &  $\beta+1$\\
\hline
$\beta^5$ & $\beta^2+\beta$\\
\hline
$\beta^6$ &  $\beta^3+\beta^2$\\
\hline
$\beta^7$ & $\beta^3+\beta+1$\\
\hline
$\beta^8$ &  $\beta^2+1$\\
\hline
$\beta^9$ & $\beta^3+\beta$\\
\hline
$\beta^{10}$ &  $\beta^2+\beta+1$\\
\hline
$\beta^{11}$ & $\beta^3+\beta^2+\beta$\\
\hline
$\beta^{12}$ &  $\beta^3+\beta^2+\beta+1$\\
\hline
$\beta^{13}$ & $\beta^3+\beta^2+1$\\
\hline
$\beta^{14}$ &  $\beta^3+1$\\
 \end{tabular}
 \label{novelTab10}
\end{table*}
 
 \begin{table*}[h]
 \caption{$23/35$ RSC, $f(x)=1+x+x^4$}
\centering
 \begin{tabular}{c c c} 
 \hline
 $a(x)$ & $b(x)$ & $h(x)$\\ [0.5ex] 
 \hline\hline
$1$ & $1+x^2+x^3+x^4$ & $1+x+x^4$\\ 
\hline
$1+x+x^2+x^3+x^5$ &  $1+x^2+x^3+x^4+x^8+x^9$ & $1+x^7+x^9$ \\
\hline
$1+x+x^2+x^3+x^5+x^7+x^8$ & $1+x^2+x^3+x^4+x^7+x^{12}$ & $1+x^{11}+x^{12}$\\
\hline
$1+x+x^4$ & $1+x+x^2+x^4+x^5+x^6+x^7+x^8$  &$1+x^2+x^8$
 \end{tabular}
 \label{novelTab11}
\end{table*}
 
 $g(x)$ is a match for Case4, ie it is made up of unique repeated roots. Upon factorizing we have $g(x)=(1+x)(1+x+x^3)$. Table \ref{novelTab12} shows the elements of GF$(2^3)$ generated by $(1+x+x^3)$ and we can confirm that there are 3 valid $(e,~f)$ pairs. However since there are no valid $(e,~f)$ pairs in GF$(2)$, it also means that there cannot be any valid $(u,~v)$ pairs and $b(x) \st w_H(\bb)=3$ does not exist.
 
 \begin{table*}[h]
 \caption{Non-zero Elements of GF$(2^3)$ generated by $1+x+x^3$}
\centering
 \begin{tabular}{c c} 
 \hline
 power & polynomial \\ [0.5ex] 
 \hline\hline
$\beta^0~=\beta^{7}=1$ & $1$\\
\hline
$\beta$ & $\beta$\\
\hline
$\beta^2$ &  $\beta^2$\\
\hline
$\beta^3$ & $\beta+1$\\
\hline
$\beta^4$ &  $\beta^2+\beta$\\
\hline
$\beta^5$ & $\beta^2+\beta+1$\\
\hline
$\beta^6$ &  $\beta^2+1$\\
 \end{tabular}
 \label{novelTab12}
\end{table*}
\end{example}



%\subsubsection{Special Case for $w_H=4$}%: Equal Repeated Polynomial Roots}
%If $w_H=4$, then $h(x) = 1+x^{u}+x^{v}+x^{w}$.
%Finding the structure of $h(x)$ when $w_H=4$ for general cases has proven to be a difficult problem for which we have not found a feasible solution to. However, there is a special case where have been able to come up with a method for determining the structure of $h(x)$. 

%\paragraph{$f(x)=1+x^{2i},~i=1,2,...$}
%Since $h(x)$ is divisible by $f(x)$, the roots of $f(x)$ are also the roots of $h(x)$. Inserting $\beta$ into $h(x)$ we get

%$$1+\beta^{u}+\beta^{v}+\beta^{w} =0$$


\subsection{Partial Structured Distance Spectrum}
The partial structured distance spectrum for the $5/7,~37/21$ and $23/35$ RSC codes are shown in Tables \ref{novelTab13},  \ref{novelTab14} and \ref{novelTab15} respectively. 
%(quarantine)%For each RSC codeThese were obtained by dividing the general form of $h(x)$ for $w_H(\bh)=2$ and ($w_H(\bh)=2$ if it exists) by $f(x)$ and multiplying it by $g(x)$ to obtain $b(x)$ for a given RSC code. This process is repeated doing the same for the general form of $b(x)$. In both cases $a(x),~b(x)$ and $h(x)$ are only added to the list if $w_H(\bc) \leq d_{\text{max}}$.

\begin{table*}[h!]
 \caption{Partial Structured Distance Spectrum for the $5/7$ RSC code,$d_{\text{max}}=8$}
\centering
 \begin{tabular}{c c c} 
 \hline
 $a(x)$ & $b(x)$ & $h(x)$ \\ [0.5ex] 
 \hline\hline
$1$ & $1+x+x^{2}$ & $1+x^2$\\
\hline
$1+x^2$ & $1+x+x^3+x^4$ & $1+x^{4}$\\
\hline
$1+x$ & $1+x^3$ & $1+x+x^2+x^3$\\
\hline
$1+x^2+x^4$ & $1+x+x^3+x^5+x^6$ & $1+x^{6}$\\
\hline
$1+x^2+x^3$ & $1+x+x^5$ & $1+x^3+x^4+x^5$\\
\hline
$1+x+x^2$ & $1+x^2+x^4$ & $1+x+x^3+x^4$\\
\hline
$1+x+x^3$ & $1+x^4+x^5$ & $1+x+x^2+x^5$\\
\hline
$1+x^2+x^4+x^6$ & $1+x+x^3+x^5+x^7+x^8$ & $1+x^8$\\
\hline
$1+x+x^3+x^4$ & $1+x^6$ & $1+x+x^2+x^4+x^5+x^6$\\
 \end{tabular}
 
 \label{novelTab13}
\end{table*}

\begin{table*}[h!]
 \caption{Partial Structured Distance Spectrum for the $37/21$ RSC code,$d_{\text{max}}=9$}
\centering
 \begin{tabular}{c c c} 
 \hline
 $a(x)$ & $b(x)$ & $h(x)$ \\ [0.5ex] 
 \hline\hline
$1+x$ & $1+x+x^{4}+x^5$ & $1+x^5$\\
\hline
$1$ & $1+x^4$ & $1+x+x^2+x^3+x^4$\\
\hline
$1+x+x^5+x^6$ & $1+x+x^4+x^6+x^9+x^{10}$ & $1+x^{10}$\\
 \end{tabular}
 
 \label{novelTab14}
\end{table*}

\begin{table*}[h!]
 \caption{Partial Structured Distance Spectrum for the $23/35$ RSC code,$d_{\text{max}}=10$}
\centering
 \begin{tabular}{c c c} 
 \hline
 $a(x)$ & $b(x)$ & $h(x)$ \\ [0.5ex] 
 \hline\hline
$1+x^2+x^3$ & $1+x^7$ & $1+x+x^2+x^6+x^7$\\
\hline
$1$ & $1+x^2+x^3+x^4$ & $1+x+x^{4}$\\
\hline
$1+x+x^2+x^3+x^5$ & $1+x^3+x^4+x^8+x^9$ & $1+x^7+x^9$\\
\hline
$1+x+x^2+x^3+x^5+x^7+x^8$ & $1+x+x^3+x^4+x^7+x^{12}$ & $1+x^{11}+x^{12}$\\
\hline
$1+x^2+x^3+x^7+x^9+x^{10}$ & $1+x^{14}$ & $1+x+x^2+x^6+x^8+x^9+x^{13}+x^{14}$\\
 \end{tabular}
 
 \label{novelTab15}
\end{table*}
\newpage
We use the partial structured distance spectrum to calculate bit-error bounds for each RSC and compare them to the bit-error bounds obtained via the distance spectrum as well as simulation results. We use probability of bit-error in doing this and a more general formula for calculating $P_b$ is shown below [4]

\begin{equation}
P_b \leq \frac{1}{k} \sum_{d=d_{\text{free}}}^{\infty} w(d) Q\Bigg( \sqrt{\frac{2dE_c}{N_0}}\Bigg)
\label{novelEq6}
\end{equation}
where $w(d)=\sum_{i=1}^{\infty} i~ a(d,i)$ and $ a(d,i)$ is the number of codewords of weight $d$ generated by an input message of weight $i$. If we set a limit on the maximum value of the codeword weight $d_{\text{max}}$
 we can rewrite (\ref{novelEq6}) as 
\begin{equation}
P_b \leq \frac{1}{k} \sum_{d=d_{\text{free}}}^{d_{\text{max}}} w(d) Q\Bigg( \sqrt{\frac{2dE_c}{N_0}}\Bigg)
\label{novelEq7}
\end{equation}
%In order to confirm the validity of our method, we use the values obtained from Tables \ref{novelTab8}, \ref{novelTab9} and \ref{novelTab10} to find the bounds for the BER of the RSC code, $P_b$.Finally, we compare the results obtained to $P_b$ found using the Transfer Function method as well as the simulation results.



